An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2023-06-13 poly-embed-journal/poly-embed-journal.tex
One final pass on edits
meeting edits

For (i), given the embedding $\varphi: \Sc\to\reals^d$, begin by linking each embedding point back to its original report, so that $\psi(\varphi(r)) = r$.
Now we wish to determine $\psi(u)$ for non-embedding points $u\in\reals^d$ which optimize $L$ for some distribution.
Let $\Gamma = \prop L$ and define $\U = \{\Gamma(p) \mid p\in\simplex\}$ to be the ``range'' of $\Gamma$, i.e., all possible optimal sets.
For each $U\in\U$, we can define $R_U = \{ r\in\Sc \mid \varphi(r) \in U\}$ to be the set of target reports which, by definition of embedding, are $\ell$-optimal when $U$ is $L$-optimal.
We would like to restrict $\psi(U) \subseteq R_U$, so that optimal surrogate reports are mapped to optimal target reports.
The challenge is that we could have a point $u\in U\cap U'$ for two optimal sets $U,U'\in\U$, and \emph{a priori}, it could be that $R_U \cap R_{U'} = \emptyset$.
The first step of the proof is to show that this scenario cannot arise.
\begin{equation}
  \label{eq:intersection-property-embedding}
  \forall \U'\subseteq\U, \; \cap_{U\in\U'} U \neq \emptyset \implies \cap_{U\in\U'} R_U \neq \emptyset~.
\end{equation}
\noindent
Thus, for any $u\in\cup\U$, we have a nonempty set of valid choices for $\psi(u)$.
(Eq.~\eqref{eq:intersection-property-embedding} may appear similar to indirect elicitation; in fact the two conditions are equivalent, as we discuss in \S~\ref{sec:poly-ie-consistency}.)

@@

\paragraph{Connections to $\H$-consistency and calibration}
\reviewertwo{Comment 1}
Throughout, we establish that embedding implies calibration when restricting to the class of polyhedral losses, and use the canonical result that calibration is equivalent to consistency to establish equivalence to consistency.
However, consistency is defined by considering the optimal hypothesis over the set of all measurable functions (see \S~\ref{app:consistency}).
However, it has been established that if the hypothesis class $\H$ is restricted, a universally consistent surrogate and link pair may not be consistent over the set $\H$, or $\H$-consistent, even in the realizable setting~\citep{long2013consistency,kuznetov2014multiclass,zhang2020bayes}.
One interesting direction is to understand if (some restricted version of) ``$\H$-embeddings'' via a polyhedral surrogate implies (1) $\H$-calibration, and (2) $\H$-consistency, which are not equivalent \citep{awasthi2021calibration,awasthi2021finer}.
\citet{awasthi2022hconsistency,awasthi2022multi} study $\H$ consistency bounds for adversarial classification and multi-class classification, though it is unclear how such bounds generalize to general finite prediction tasks.

>>>>

For (i), given the embedding $\varphi: \Sc\to\reals^d$, begin by linking each embedding point back to its original report, so that $\psi(\varphi(r)) = r$.
Now we wish to determine $\psi(u)$ for non-embedding points $u\in\reals^d$ which optimize $L$ for some distribution.
Let $\Gamma = \prop L$ and define $\U = \{\Gamma(p) \mid p\in\simplex\}$ to be the ``range'' of $\Gamma$, i.e., all possible optimal sets.
For each $U\in\U$, we can define $R_U = \{ r\in\Sc \mid \varphi(r) \in U\}$ to be the set of target reports which, by definition of embedding, are $\ell$-optimal when $U$ is $L$-optimal.
We would like to restrict $\psi(U) \subseteq R_U$, so that optimal surrogate reports are mapped to optimal target reports.
The challenge is that we could have a point $u\in U\cap U'$ for two optimal sets $U,U'\in\U$, and \emph{a priori}, it could be that $R_U \cap R_{U'} = \emptyset$.
The first step of the proof is to show that this scenario cannot arise.
\begin{equation}
  \label{eq:intersection-property-embedding}
  \forall \U'\subseteq\U, \; \cap_{U\in\U'} U \neq \emptyset \implies \cap_{U\in\U'} R_U \neq \emptyset~.
\end{equation}
\noindent
Thus, for any $u\in\cup_{U \in \U}U$, we have a nonempty set of valid choices for $\psi(u)$.
(Eq.~\eqref{eq:intersection-property-embedding} may appear similar to indirect elicitation; in fact the two conditions are equivalent, as we discuss in \S~\ref{sec:poly-ie-consistency}.)

@@

\paragraph{Connections to $\H$-consistency and calibration}
\reviewertwo{Comment 1}
Throughout, we rely heavily on the fact that, when the hypothesis class $\H$ in question is the set of all measurable functions, then calibration is equivalent to consistency.
% However, consistency is defined by considering the optimal hypothesis over the set of all measurable functions (see \S~\ref{app:consistency}).
Calibration is no longer equivalent to consistency, however, when the hypothesis class $\H$ is restricted.
Consistency in this case is called \emph{$\H$-consistency}.
Calibration can fail to be sufficent for $\H$-consistency even in the realizable setting~\citep{long2013consistency,kuznetov2014multiclass,zhang2020bayes}.
One interesting direction is to understand if (some restricted version of) ``$\H$-embeddings'' via a polyhedral surrogate implies (1) $\H$-calibration, and (2) $\H$-consistency, which are not equivalent \citep{awasthi2021calibration,awasthi2021finer}.
\citet{awasthi2022hconsistency,awasthi2022multi} study $\H$ consistency bounds for adversarial classification and multi-class classification, though it is unclear how such bounds generalize to general finite prediction tasks.

### 2023-06-13 poly-embed-journal/reviews/jmlr-response.tex
meeting edits

We thank the reviewer for their thoughtful review and careful reading of our work. We have incorporated the editing suggestions made, and marked in our revised manuscript where non-typo changes to the text were made. 
Below we respond to some of the clarifying questions:
\begin{enumerate}
	\item \emph{Clarify the point that indirect elicitation is strictly weaker than calibration}

@@

	\item \emph{Proof of Lemma~\ref{lem:polyhedral-range-gamma}}

@@

	\item \emph{``Thus, for any $u \in \cup \mathcal{U}$''}

	Each element of $\mathcal{U}$ is a set, so the union $\cup \mathcal{U}$ is a  bit imprecise; we clarify that we are discussing $u \in \bigcup_{U \in \mathcal{U}} U$.
\end{enumerate}

>>>>

We thank the reviewer for their thoughtful review and careful reading of our work. We have incorporated the editing suggestions made, and marked in our revised manuscript where non-typo changes to the text were made. 
Below we respond to some of the clarifying questions:
\begin{enumerate}
	\item \emph{Clarify the point that indirect elicitation is strictly weaker than calibration.}

@@

	\item \emph{Proof of Lemma~\ref{lem:polyhedral-range-gamma}; several suggestions for clarity.}

@@

	\item \emph{``Thus, for any $u \in \cup \mathcal{U}$''; potential typo.}

	This is actually not a typo, but we expanded the notation to be more explicit: $u \in \bigcup_{U \in \mathcal{U}} U$.
\end{enumerate}
